\myTitle

### 2024-10-31 tex/body-text-of-paper.tex
fix the citealts

Genetic markers have long been used in the
management of Pacific salmon, and salmon conservation and management have been
at the forefront of a number of advances in molecular ecology,
from data generation techniques \citep{clemento2011discovery,campbell2015genotyping,mckinney2017managing,baetscher2018microhaplotypes}
to statistical methodology
\citep{smouse1990genetic,anderson2002model,pella2006gibbs,anderson2010assessing}.
Two broadly applicable techniques that have been
actively fostered by the Pacific salmon research community are genetic
stock identification
(GSI:~\citealt{milner1982genetic,beacham2004dna,seeb2007development})
and parentage based tagging
(PBT:~\citealt{anderson2006power, garza2007large, abadia2013large, steele2013validation}).

@@

For the candidate markers found by the above process, we designed amplification primers using
Primer3 \citep{koressaar2007enhancements,untergasser2012primer3} and tested amplification in a
subset of Chinook salmon
samples. The primer pairs that amplified sequence that reliably mapped back to the association-peak region were then typed
in a separate collection of 1,638 Sacramento River Chinook salmon sampled from the fish trap below Keswick Dam, including 1,169 winter run, 281 spring
run, and 188 fall/late-fall run. We divided the fish identified as fall/late-fall (via the 125-locus genetic
stock identification data set of \citealt{thompson2020complex} into fall run and late-fall run according
to their sampling date at Keswick:  99 fish arriving before Dec 26 were classified as fall run and 89 fish arriving after Dec 26 were
classified as late-fall run.   The allele frequencies of the target SNPs at the remaining amplicons
were
estimated for each of these four groups: winter, spring, fall, and late-fall, and we retained
amplicons showing large allele frequency differences between late-fall fish and all other runs.

@@

We include a marker that targets the sex-determining region ({\em sdY} on the Y chromosome in Chinook salmon.
This marker characterizes genetic sex in Central Valley populations \comment{\citep{von2015development}}.
And, finally, we include marker Ots\_coho001\_05\_32691399 which is fixed for alternate alleles in
coho salmon and Chinook salmon.  This is helpful when samplers have unwitting
collected coho salmon from ocean catches.

@@

For evaluation of candidate loci, dual-barcoded sequences were used
to identify individual tissue samples using the MiSeq analysis software (Illumina).
The paired-end sequence reads were joined together using Fast Length Adjustment
of SHort reads (FLASH: \citealt{magovc2011flash}) and mapped to an indexed sequence reference created from the Stacks target loci using BWA (Li and Durbin 2010). Mapped reads were converted to BAM files using SAMtools (Li et al. 2009) and freebayes (Garrison and Marth 2012) was used to call variants.

@@

Each locus was assessed for the presence of null alleles using the R package `whoa'
(\url{https://github.com/eriqande/whoa}; {\em see} \citealt{hendricks2018recent}).

@@

Finally, we investigated the matrix of assignments and misassignments
broken down according to the genotype of the fish at the markers within
the RoSA.  For this we identified the RoSA genotype (EE, EL, or LL, see
\citealt{thompson2020complex}) from the concordance of the genotypes
at all 8 markers described in \citep{thompson2020complex}, requiring no missing
data at any of those 8 markers, and discarding data from 12 individuals
in which the E or L haplotypes had clearly recombined.

>>>>

Genetic markers have long been used in the
management of Pacific salmon, and salmon conservation and management have been
at the forefront of a number of advances in molecular ecology,
from data generation techniques \citep{clemento2011discovery,campbell2015genotyping,mckinney2017managing,baetscher2018microhaplotypes}
to statistical methodology
\citep{smouse1990genetic,anderson2002model,pella2006gibbs,anderson2010assessing}.
Two broadly applicable techniques that have been
actively fostered by the Pacific salmon research community are genetic
stock identification
\citep[GSI:~][]{milner1982genetic,beacham2004dna,seeb2007development}
and parentage based tagging
\citep[PBT:~][]{anderson2006power, garza2007large, abadia2013large, steele2013validation}.

@@

For the candidate markers found by the above process, we designed amplification primers using
Primer3 \citep{koressaar2007enhancements,untergasser2012primer3} and tested amplification in a
subset of Chinook salmon
samples. The primer pairs that amplified sequence that reliably mapped back to the association-peak region were then typed
in a separate collection of 1,638 Sacramento River Chinook salmon sampled from the fish trap below Keswick Dam, including 1,169 winter run, 281 spring
run, and 188 fall/late-fall run. We divided the fish identified
from the 125-locus genetic
stock identification data set of \citet{thompson2020complex}  as fall/late-fall into fall run and late-fall run according
to their sampling date at Keswick:  99 fish arriving before Dec 26 were classified as fall run and 89 fish arriving after Dec 26 were
classified as late-fall run.   The allele frequencies of the target SNPs at the remaining amplicons
were
estimated for each of these four groups: winter, spring, fall, and late-fall, and we retained
amplicons showing large allele frequency differences between late-fall fish and all other runs.

@@

We include a marker that targets the sex-determining region ({\em sdY}) on the Y chromosome in Chinook salmon.
This marker characterizes genetic sex in Central Valley populations \comment{\citep{von2015development}}.
And, finally, we include marker Ots\_coho001\_05\_32691399 which is fixed for alternate alleles in
coho salmon and Chinook salmon.  This is helpful when samplers have unwitting
collected coho salmon from ocean catches.

@@

For evaluation of candidate loci, dual-barcoded sequences were used
to identify individual tissue samples using the MiSeq analysis software (Illumina).
The paired-end sequence reads were joined together using Fast Length Adjustment
of SHort reads \citep[FLASH:~][]{magovc2011flash}) and mapped to an indexed sequence reference created from the Stacks target loci using BWA (Li and Durbin 2010). Mapped reads were converted to BAM files using SAMtools (Li et al. 2009) and freebayes (Garrison and Marth 2012) was used to call variants.

@@

Each locus was assessed for the presence of null alleles using the R package `whoa'
\citep[\url{https://github.com/eriqande/whoa};  see][]{hendricks2018recent}.

@@

Finally, we investigated the matrix of assignments and misassignments
broken down according to the genotype of the fish at the markers within
the RoSA.  For this we identified the RoSA genotype \citep[EE, EL, or LL, see~][]{thompson2020complex} from the concordance of the genotypes
at all 8 markers described in \citep{thompson2020complex}, requiring no missing
data at any of those 8 markers, and discarding data from 12 individuals
in which the E or L haplotypes had clearly recombined.
